Automated Topic Naming

### 2012-01-19 ese/ese.tex
explained IRR a little better

To evaluate our results empirically, we compared them to the annotations that would result if the seven labels
 were applied randomly. In the first simulation
we sampled with replacement from our own NFR label distributions to
produce random ratings that looked like our own. We then applied the
Kappa-statistic on this sampling, compared it with our labelling, and repeated
this 100,000 times. We found that
for 4 out of 7 NFR labels, the IRR values for our labels were greater than the random
IRR measures 96\% of the time. For \emph{portability} and \emph{efficiency}, our IRR
was greater 100\% of the time both for Neil's ratings, Abram's ratings
and the union of both Neil and Abram. One explanation of the positive result for \emph{portability} is that such changes are often 
accompanied by clear indicator terms such as \emph{Windows, Linux, SunOS}, etc.

Figure \ref{fig:irr} depicts the IRR of
these sampled ratings versus our IRR using the Kappa statistic. We also achieved similar results if the ratings were pulled from
uniform distributions. These experiments indicate that our labels and
ratings were an improvement on random annotations in all cases, with the exceptions of \emph{functionality},
\emph{reliability} and \emph{usability}.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/self-sample-Both}
  \caption{Measured IRR versus IRR of labeling random simulations. Perfect IRR is 1.0. }
  \label{fig:irr}
\end{figure}

>>>>

To evaluate our results empirically, we compared them to the annotations that would result if the seven labels
 were applied randomly. In the first simulation, as shown by Figure \ref{fig:irr},
we sampled with replacement from our own NFR label distributions to
produce random ratings that looked like our own. We then applied the
Kappa-statistic on this sampling and our labelling, and repeated
this 100,000 times. We then compared this distribution of simulated
IRR ratings against our our IRR scores. We found that
for 4 out of 7 NFR labels, the IRR values for our labels were greater than the random
IRR measures 96\% of the time. For \emph{portability} and \emph{efficiency}, our IRR
was greater 100\% of the time both for Neil's ratings, Abram's ratings
and the union of both Neil and Abram. 
We know this by evaluating our IRR ratings against the empirical
cumulative distribution function (ECDF) of the IRR ratings of the 100,000
simulation runs.
One explanation of the positive result for \emph{portability} is that such changes are often 
accompanied by clear indicator terms such as \emph{Windows, Linux, SunOS}, etc.

Figure \ref{fig:irr} depicts the IRR of
these simulated sampled ratings versus our IRR using the Kappa statistic. We also achieved similar results if the ratings were pulled from
uniform distributions. These experiments indicate that our labels and
ratings were an improvement on random annotations in all cases, with the exceptions of \emph{functionality},
\emph{reliability} and \emph{usability}.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/self-sample-Both}
  \caption{Measured IRR versus IRR of random labeling
    simulations. Perfect IRR is 1.0.
    The red line and points highlight the inter-rater reliability of
    NFR topics labels
    measured on PostgreSQL. 
    The box-plots are the distribution of 100,000 IRR ratings between
    random simulation, drawn from our distribution of ratings, and our
    labelling of NFRs.
    Note how for 4 of the 7 NFRs it is
    distinctly higher than the median of the simulations.
  }
  \label{fig:irr}
\end{figure}
